Attrition in Online Learning: Understanding Persistence and Dropout in Massive Open Online Courses

### 2014-10-26 paper_v1.Rnw
added intro to study 2

To gain a better understanding of the attrition patterns identified in Study 1, we designed a smaller, more focused follow-up study. In Study 2, we reached out to learners who were likely to drop out of a course and asked them to provide feedback. We developed a predictive model to identify learners who were likely to drop out and ask them to complete a survey.

\begin{description}
  \item[H4a] Learners who report having `not enough time' can be divided into those with too many higher priority obligations (work, school, family) and those with low volition.
  \item[H4b] Learners who do not report specific obligations (e.g., work, school, family) tend to fall in the low volition than in the high-priority obligations group, and vice versa.
\end{description}

>>>>

To gain a better understanding of the attrition patterns identified in Study 1, we designed a smaller, more focused follow-up study. In Study 2, we reached out to learners who were likely to drop out of a course and asked them to provide feedback. To this end, we developed a predictive model to identify at-risk learners and asked them to complete a survey. One goal of this study was to further investiage research question $RQ3a$ based on learners' own descriptions of the challenges they faced. Specifically, in Study 1, most learners reported that they disengaged due to a shortage of time. A variety of factors can influence the amount of time learners have at their disposal. Higher priority obligations, such as professional, academic, and personal committments, are certainly large contributors. Another critical factor, especially in the context of MOOCs as largely unguided learning environments, is learners' volitional control to engage in self-regulated learning \cite{corno2001volitional}. For instance, learners' ability to allocate time for the course in the presence of potential distractors of subjectively lower importance than taking the course (e.g., watching TV). We constructed the following hypotheses about the presence of these two factors for learners who report having not enough time:

\begin{description}
  \item[H4a] Learners who report having `not enough time' can be grouped into those with higher priority obligations (professional, academic, personal) and those with low volitional control.
  \item[H4b] Learners who do not report specific higher-priority obligations tend to exhibit lower volitional control than those who specify particular obligations.
\end{description}

Another goal of Study 2 was to collect data to test hypotheses $H1, H2, H3$ on the role of goal striving, social belonging, and growth mindset in the success of MOOC learners. To this end, we included a self-report measures for each construct in the survey that was sent out to at-risk learners.
